Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added figures to TW and IGBW

\chapter{Instrumented Calibration (non-combustible) Wall Experiments}
Purpose

\section{Experimental Arrangement}
A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.

@@

>>>>

\chapter{Instrumented Calibration (non-combustible) Wall Experiments}
Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.  In these experiments the target is a non-combustible wall and therefore the wall will not contribute to the fire.  The fires were initially placed at predetermined, fixed positions away from the wall.  In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel. Starting at a position where the closest edge of the burner was two burner widths from the wall. The burner was moved toward the wall until the burner was against the wall.

\section{Experimental Arrangement}
A free standing steel frame wall with a 12.7 mm thick, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_NC_Wall}\\
	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall. Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
	\label{Instrumented_NC_Wall}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall. Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
	\label{Instrumented_GB_Wall}
\end{figure}
